Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-07-30 surfaces-write-up/surface-write-up.tex
made bibtex work

The work in this paper may help calculate a presentation of certain rings of
Hilbert 
modular forms and Siegel modular forms. Recall that Hilbert and Siegel 
modular forms are both generalizations of modular forms to higher dimensions,
as described in \cite{geer:siegel-moduar} and \cite{bruinier:hilbert-modular}.
By a result by Voight and Zureick-Brown \cite[Proposition 6.1.5]{vzb:stacky}, 
one can translate the analytic category of 1-dimensional complex orbifolds to
the algebraic category of stacky curves. 
We expect that one can generalize this result to yield an equivalence of
categories between an appropriate subcategory of $m$-dimensional orbifolds and
a subcategory of $m$-dimensional algebraic spaces.
In particular, this would allow us to translate rings of Hilbert modular forms
and Siegel modular forms whose coarse space is a projective space or a
Hirzebruch surface to canonical rings on the corresponding algebraic surfaces.
Thereby, our techniques would give a bound on generators and relations for
Hilbert and Siegel modular forms with certain underlying spaces.

>>>>

The work in this paper may help calculate a presentation of certain rings of
Hilbert 
modular forms and Siegel modular forms. Recall that Hilbert and Siegel 
modular forms are both generalizations of modular forms to higher dimensions,
as described in \cite{geer:siegel-modular} and \cite{bruinier:hilbert-modular}.
By a result by Voight and Zureick-Brown \cite[Proposition 6.1.5]{vzb:stacky}, 
one can translate the analytic category of 1-dimensional complex orbifolds to
the algebraic category of stacky curves. 
We expect that one can generalize this result to yield an equivalence of
categories between an appropriate subcategory of $m$-dimensional orbifolds and
a subcategory of $m$-dimensional algebraic spaces.
In particular, this would allow us to translate rings of Hilbert modular forms
and Siegel modular forms whose coarse space is a projective space or a
Hirzebruch surface to canonical rings on the corresponding algebraic surfaces.
Thereby, our techniques would give a bound on generators and relations for
Hilbert and Siegel modular forms with certain underlying spaces.
